Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-11 manuscript/manuscript.Rmd
took our sure and col functions for probe

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated `r nSims` times. Note that the y-axes vary across panels.", fig.width=5, fig.height=6, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_ResidualsFullModel.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(yearDiff))

>>>>

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated `r nSims` times. Note that the y-axes vary across panels.", fig.width=5, fig.height=6, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/oneStepResultsFull.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(resids),
               sdDiff = sd(resids),
               dnDiff = quantile(resids, probs = 0.025, names=FALSE),
               upDiff = quantile(resids, probs = 0.975, names=FALSE))
ggplot(diffD)+
  geom_hline(aes(yintercept=0), linetype=2, color="grey50")+
  geom_point(aes(x=year, y=avgDiff), size=3)+
#   geom_errorbar(aes(x=year, ymax=avgDiff+sdDiff, ymin=avgDiff-sdDiff), width=0.1)+
    geom_errorbar(aes(x=year, ymax=upDiff, ymin=dnDiff), width=0.1)+
  facet_grid(species~., scales = "free_y")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
